$R^*$: A robust MCMC convergence diagnostic with uncertainty via gradient-boosted machines

### 2020-03-16 write_up/ms.tex
draft of text waiting for mvt normal case

\subsection{Lack of convergence of the joint distribution: multivariate normal model}\label{sec:multivariate_normal}
Simple AR1 example followed by 250 MVT normal.

>>>>

\subsection{Lack of convergence of the joint distribution: multivariate normal model}\label{sec:multivariate_normal}
In this example, we use the 250-dimensional multivariate normal target, where its precision matrix is generated from a Wishart distribution \cite{hoffman2014no}. We assume that the Wishart distribution's degrees of freedom parameter is 250, resulting in a distribution with high correlations between dimensions. We use Stan's NUTS algorithm to sample from this target distribution, and run the algorithm for X iterations: at this point, all the $\hat{R}<1.01$ and the effective sample size for each dimension exceeded 400 (recommendations from \cite{vehtari2019rank}). Using these samples, we used Algorithm \ref{alg:R_star_uncertainty} to generate an uncertainty distribution for $R^*$, which is shown in Fig. X.
